---
title: "Assignment 3"
author: "Niharika Dobanaboina"
date: "2022-10-17"
output: pdf_document
align: center
---

\newpage
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tinytex)
```

\textcolor{blue}{\textbf{\underline{Reading the CSV file:}}}

```{r}

UniversalBank<- read.csv("UniversalBank.csv")
head(UniversalBank)
```
\textcolor{blue}{\textbf{\underline{Converting PersonalLoan,Online,CreditCard variables to factors:}}}

```{r}
UniversalBank$PersonalLoan<-as.factor(UniversalBank$PersonalLoan)
UniversalBank$Online<-as.factor(UniversalBank$Online)
UniversalBank$CreditCard<-as.factor(UniversalBank$CreditCard)

```

\textcolor{blue}{\textbf{\underline{Splitting data into Training and Validation sets:}}}

```{r}
set.seed(345)
library(caret)

Split_data<-createDataPartition(UniversalBank$PersonalLoan,p=.6,list=FALSE,times=1)
Training_set<-UniversalBank[Split_data,]
Validation_set<-UniversalBank[-Split_data,]

```

\textcolor{blue}{\textbf{\underline{Normalizing training and Validation set:}}}

```{r}

Normalization<-preProcess(Training_set[,-c(10,13,14)],method=c("center","scale"))

Training_norm<-predict(Normalization,Training_set)
Validation_norm<-predict(Normalization,Validation_set)

```
\newpage
\textcolor{blue}{\textbf{\underline{A. Creating a pivot table for the training data with CreditCard as a row variable, PersonalLoan as a}}}
\textcolor{blue}{\textbf{\underline{secondary row variable and Online as a column variable:}}}


```{r}

table_1<-table(Training_norm$CreditCard,Training_norm$PersonalLoan,Training_norm$Online)
View(table_1)

prop_table1<-prop.table(table_1)

View(prop_table1)

```

\textcolor{blue}{\textbf{\underline{B. Probabality of a customer accepting the loan offer who owns a credit card and is also actively using}}}
\textcolor{blue}{\textbf{\underline{online banking services:}}}

$$\text{From the Pivot table in A,}$$
$$ P(Loan=1|CreditCard=1,Online=1) = 52/(52+495) = 0.095 $$

\textcolor{blue}{\textbf{\underline{C. Creating a Pivot table having Loan as a row variable and CreditCard as column Variable:}}}

```{r}

table_loan_cc <- table(Training_norm$PersonalLoan,Training_norm$CreditCard)
View(table_loan_cc)

```

\textcolor{blue}{\textbf{\underline{C. Creating a Pivot table having Loan as a row variable and Online as column Variable:}}}

```{r}

table_loan_online <- with(Training_norm,table(PersonalLoan,Online))
View(table_loan_online)

```

\textcolor{blue}{\textbf{\underline{D. (i)P(CC=1|Loan=1):}}}

$$ P(CC=1\cap Loan=1)/P(Loan=1)=86/288 = 0.2986$$
\textcolor{blue}{\textbf{\underline{D. (ii.)P(Online=1| Loan=1):}}}

$$ P(Online=1 \cap Loan=1)/P(Loan=1) = 176/288 = 0.6111 $$
\textcolor{blue}{\textbf{\underline{D. (iii.) P(Loan=1):}}}

```{r}

table_loan <- table(Training_norm$PersonalLoan)
View(table_loan)

prop_loan<-prop.table(table_loan)
View(prop_loan)

```

$$P(Loan=1) = 0.096 $$
\textcolor{blue}{\textbf{\underline{D. (iv.) P(CC=1|Loan=0):}}}
$$P(CC=1 \cap Loan=0)/P(Loan=0) = 820/271 = 0.3023$$
\textcolor{blue}{\textbf{\underline{D. (v.) P(Online=1|Loan=0):}}}

$$P(Online=1 \cap Loan=0)/P(Loan=0) = 0.5896$$
\textcolor{blue}{\textbf{\underline{D. (vi.) P(Loan=0):}}}

$$P(Loan=0)=0.904$$
\textcolor{blue}{\textbf{\underline{E. Computing Naive Bayes probablitity:}}}

$$P(Loan=1|CC=1,Online=1) = $$
$$= P(CC=1|Loan=1) * P(Online=1|Loan=1)*P(Loan=1)/P(CC=1|Loan=1 *) P(Online=1|Loan=1)*$$
$$P(Loan=1)+P(CC=1|Loan=0) * P(Online=1|Loan=0) *P(Loan=0)$$
$$ = 0.2986 * 0.6111 * 0.096/(0.2986 * 0.6111 * 0.096 + 0.3023 * 0.5896 * 0.904) $$
$$ = 0.09802$$
$$Therefore, P(Loan=1|CC=1,Online=1) = 0.09802$$
\textcolor{blue}{\textbf{\underline{F. Comparison of P(Loan=1|CC=1,Online=1}}}

$$\text{Upon comparing the above computed Naive Bayes Probablity with the value obtained in B,}$$
$$ \text{it can be observed that both the values are closely same.However,the probablity obtained}$$  $$\text{in B is more precise as it is calculated directly from the frequency tables based on the count.}$$
\textcolor{blue}{\textbf{\underline{G. Naive Bayes Probablity:}}}

```{r}
library(e1071)

nb_model<-naiveBayes(PersonalLoan~Online+CreditCard,data=Training_norm)
nb_model


```


$$\text{Comparing this value with the probablity obtained in (E), Naive Bayes calculates}$$
$$\text{probablities considering conditional independence. Therefore, the probablity calculated in (G) is more accurate.}$$
